Paper Figures and Text

### 2024-03-20 Fish Data Analysis/Paper_Figures.qmd
Small graph fixes

nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("NND Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Polarity Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Speed Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Numebr of Groups Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

@@

single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all)

t.test(single_perp_angle_df_middle$Fish1_Yaw_Heading_PS)

single_plot <- ggplot(single_perp_angle_graphing, aes(x = rad2deg(Fish1_Yaw_Heading_PS), fill = Label))+
  geom_histogram(aes(y=0.5*..density..),binwidth=45,position='identity', alpha = 0.5)+
  theme_classic()+
  scale_fill_manual(values = c("#CE2414","#138EC2"))+
  ylab("Proportion of Values")+
  xlab("Turning Angle (Degrees / s)")+
  xlim(-200,200)

>>>>

nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("NND Autocorrelation")+
  xlab("Offset")+
  theme_classic()+ 
  theme(legend.position = "none")

polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Polarity Autocorrelation")+
  xlab("Offset")+
  theme_classic()+ 
  theme(legend.position = "none")

speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Speed Autocorrelation")+
  xlab("Offset")+
  theme_classic()+ 
  theme(legend.position = "none")

groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Numebr of Groups Autocorrelation")+
  xlab("Offset")+
  theme_classic()+ 
  theme(legend.position = "none")

@@

single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all) %>%
                              mutate(Rounded_Turning = round_any(Fish1_Yaw_Heading_PS, pi/6)) %>%
                              group_by(Label) %>%
                              mutate(group_n = n()) %>%
                              ungroup() %>%
                              group_by(Label,Rounded_Turning,group_n) %>%
                              summarise(perc = mean(n()/group_n*100)) %>%
                              ungroup()

t.test(single_perp_angle_df_all$Fish1_Yaw_Heading_PS)
t.test(single_perp_angle_df_middle$Fish1_Yaw_Heading_PS)

single_plot <- ggplot(single_perp_angle_graphing, aes(x = rad2deg(Rounded_Turning), y = perc, fill = Label))+
  #geom_histogram(aes(y=0.5*..density..*100),binwidth=45,position='identity', alpha = 0.5)+
  geom_col(position='identity',alpha = 0.5)+
  theme_classic()+
  scale_fill_manual(values = c("#CE2414","#138EC2"))+
  ylab("Percentage of Values")+
  xlab("Turning Angle Rate (Degrees / s)")+
  xlim(-200,200)+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))
